Only the store can save you now:\\Updates and vulnerabilities on Android

### 2015-04-09 securityupdates.tex
spell check
Add Oliver Chick to the Acknowledgements

Unfortunately, whilst these tools were successful in finding malware, such techniques are not perfect.
The Malware Genome project collected 1\,260 malware samples from 2010--2011~\cite{Zhou2012b} and found a best case anti-malware detection rate of 79.6\%.
Similarly, DroidChameleon found that antivirus products could not detect malware if the binary was automatically permuted~\cite{Rastogi2013}.
Therefore detecting risky apps which might contain critical vulnerabilities is a useful tool, but it does not replace the need to provide security updates.

@@

\identifying{
\section*{Acknowledgements}
Thanks to: Richard Clayton, the mobile security reading group and Anil Madhavapeddy for reading drafts;
David Robertson for statistical advice;
and Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities.
We were funded by the EPSRC and Google but the the work presented here does not necessarily reflect their views.
}

>>>>

Unfortunately, whilst these tools were successful in finding malware, such techniques are not perfect.
The Malware Genome project collected 1\,260 malware samples from 2010--2011~\cite{Zhou2012b} and found a best case anti-malware detection rate of 79.6\%.
Similarly, DroidChameleon found that anti-virus products could not detect malware if the binary was automatically permuted~\cite{Rastogi2013}.
Therefore detecting risky apps which might contain critical vulnerabilities is a useful tool, but it does not replace the need to provide security updates.

@@

\identifying{
\section*{Acknowledgements}
Thanks to: Richard Clayton, the mobile security reading group, Anil Madhavapeddy and Oliver Chick for reading drafts;
David Robertson for statistical advice;
and Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities.
We were funded by the EPSRC and Google but the the work presented here does not necessarily reflect their views.
}
